Coherence between subjective feeling and facial expression: A comparison of human and automatic recognition

### 2019-04-05 ACII_2019_paper/ACII_2019_paper.Rmd
corr_test

```{r confusionMatrix_hr_ar, fig.height=5, fig.cap="\\label{fig:confusionMatrix_hr_ar}Comparison between the human observers and automatic classifier recognition for the classfication of emotion labels."}
comparison_hr_ar <- dplyr::inner_join(human_recognition_score,automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character,as.factor)

@@

confusionMatrix_hr_ar_freq %>% 
  ggplot(mapping = aes(x = hr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_hr), colour = "white") +
  geom_text(
    aes(label = paste0(scales::percent(prop_hr), "\n(", Freq,"/",n_hr, ")")),
    color = "black",
    size = 4,
    family="serif",
    parse = FALSE,
    lineheight = 0.7)+
  scale_fill_gradient(
    name = "Proportion of Recognized\nEmotion",
    low = "white", 
    high = "red", 
    labels = scales::percent,
    limits = c(0,1)
  ) +
  scale_x_discrete(name = "Human Observers") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(text = element_text(size=16,family="serif"),
        axis.text.x = element_text(size=16, angle = 45, hjust = 0.75,vjust=0.9),
        axis.text.y = element_text(size=16, hjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        legend.text = element_text(size=8),
        legend.position = "bottom")
```

>>>>

```{r confusionMatrix_hr_ar, fig.height=5, fig.cap="\\label{fig:confusionMatrix_hr_ar}Proportion of emotion labels classified by human observers which are recognized by the automatif classifier."}
comparison_hr_ar <- dplyr::inner_join(human_recognition_score,automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character,as.factor)

@@

confusionMatrix_hr_ar_freq %>% 
  ggplot(mapping = aes(x = hr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_hr), colour = "white") +
  geom_text(
    aes(label = paste0(scales::percent(prop_hr), "\n(", Freq,"/",n_hr, ")")),
    color = "black",
    size = 4,
    family="serif",
    parse = FALSE,
    lineheight = 0.7)+
  scale_fill_gradient(
    name = "Proportion Recognized Emotion",
    low = "white", 
    high = "red", 
    labels = scales::percent,
    limits = c(0,1)
  ) +
  scale_x_discrete(name = "Human Observers") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(text = element_text(size=16,family="serif"),
        axis.text.x = element_text(size=16, angle = 45, hjust = 0.75,vjust=0.9),
        axis.text.y = element_text(size=16, hjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        legend.text = element_text(size=8),
        legend.position = "bottom")
```

### 2019-04-05 ACII_2019_paper/ACII_2019_paper.tex
corr_test

\begin{figure}
\centering
\includegraphics{ACII_2019_paper_files/figure-latex/confusionMatrix_hr_ar-1.pdf}
\caption{\label{fig:confusionMatrix_hr_ar}Comparison between the human
observers and automatic classifier recognition for the classfication of
emotion labels.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{ACII_2019_paper_files/figure-latex/confusionMatrix_hr_ar-1.pdf}
\caption{\label{fig:confusionMatrix_hr_ar}Proportion of emotion labels
classified by human observers which are recognized by the automatif
classifier.}
\end{figure}
